Certified Desugaring of Javascript Programs using Coq

### 2016-12-12 paper/paper.tex
looking at the things to show from the Coq

\usepackage{amsmath}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}
\usepackage{listings,lstlangcoq}

@@

@@

For the purpose of relating the two semantics, we first
developed a formalization of the \lambdajs core language.
This was necessary because no such formalization existed previously;
a formalization of the original, ES3-based \lambdajs
was available,\footnote{\url{https://github.com/brownplt/LambdaJS}}
but the two versions of \lambdajs differ too much for this
to be useful.

@@

@@

@@

@@

For the proof, we also need to keep track of certain invariants,
which state that, e.g., the JavaScript objects and their
\lambdajs representations are correctly formed. 
The invariants are split into two relations, where one
involves the evaluation contexts, and the other -- the heaps.
Both of these involve the bisimulation relation, but the
context invariant uses it only positively. As the bisimulation
relation only grows during the evaluation (as new objects
are created), this makes it possible to keep the proofs simple.

@@

We prove many lemmas about the different language constructs
of JavaScript, including the internal ``specification functions''
(e.g., type conversions, operations on objects and environment
records, etc.). Typically, the proof for a lemma consists of
a series of forward reasoning steps and case analyses, and ends with
constructing a JSCert semantics derivation and proving that
the invariants were preserved. The forward reasoning is largely
automated using domain-specific tactics; the JSCert derivation
is constructed using the \texttt{eauto} tactic with a specialized
hint database (\texttt{nocore} is used to avoid using the standard
hints coming from Coq and Chargu\'eraud's TLC
library\footnote{\url{http://www.chargueraud.org/softs/tlc/}}, which is
used both by JSCert and our development).

@@

In the course of our work, we found numerous cases where
\lambdajs did not faithfully follow the ES5 
specification\footnote{\url{https://github.com/tilk/LambdaCert/wiki/Issues-with-LambdaS5}}.
Some of these issues were serious enough that
far-reaching changes in the \lambdajs environment were needed
to solve them. Interestingly, no serious issues in JSCert were
found, which strengthens our confidence that it accurately models
the ES5 specification.

While proving the correctness of while loops, we found an interesting
inconsistency between the ES5 specification and the behavior
of the two most popular JavaScript implementations, Google's V5 and
Mozilla's SpiderMonkey. The discovery of the inconsistency,
which involves exceptions and statement result values,
resulted in a correction being made in the official ES6
specification\footnote{\url{https://esdiscuss.org/topic/loop-unrolling-and-completion-values-in-es6}}.

@@

>>>>

\usepackage{amsmath}
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}

@@

\usepackage{minted}

@@

For the purpose of relating the two semantics, we first developed a
formalization of the \lambdajs core language. This was necessary because no such
formalization existed previously; a formalization of the original, ES3-based
\lambdajs was available,\as{I propose we use biblatex and add bib references for
  urls instead of
  footnotes.}\footnote{\url{https://github.com/brownplt/LambdaJS}} but the two
versions of \lambdajs differ too much for this to be useful.

@@

\begin{minted}{coq}
Inductive resultof (T : Type) : Type :=
| result_some : T -> resultof T
| result_fail : string -> resultof T        (* program error *)
| result_impossible : string -> resultof T  (* inconsistency *)
| result_bottom : resultof T                (* out of fuel *)
| result_dump : ctx -> store -> resultof T  (* dump state *)

Definition eval runs c st (e : expr) : result :=
  let return_value := result_value st in
  match e with
  | expr_empty => return_value value_empty
  | expr_undefined => return_value value_undefined
...

Record runs_type : Type := runs_type_intro {
    runs_type_eval : ctx -> store -> expr -> result
}.

Definition runs_0 := {|
    runs_type_eval := fun c st _ => result_bottom
  |}
.

Definition runs_S runs := 
  let wrap {A : Type} (f : runs_type -> ctx -> store -> A) c st : A :=
    f runs c st
  in {|
    runs_type_eval := wrap eval
  |}
.

Fixpoint runs max_step : runs_type :=
  match max_step with
  | 0 => runs_0
  | S max_step' => runs_S (runs max_step')
  end
.

Lemma eval_complete : forall c st e o,
  red_expr c st e o -> 
  exists k, runs_type_eval (runs k) c st e = result_some o.

Record runs_type_correct runs :=
    make_runs_type_correct {
        runs_type_correct_eval : forall c st e o,
            runs_type_eval runs c st e = result_some o -> red_expr c st e o
}.

Lemma eval_correct : forall runs c st e o,
  runs_type_correct runs -> 
  eval runs c st e = result_some o ->
  red_expr c st e o.

Lemma runs_correct : forall k, runs_type_correct (runs k). 
\end{minted}

\asi{Add the theorem.}

@@

\asi{Put a forward pointer to a section where we described the issue in more
  details.}

@@

\asi{we should put a code snippet of the environment here. Also, do we want to
  talk more about the OCaml tool used to generate it?}

@@

For the proof, we also need to keep track of certain invariants, which state
that, e.g., the JavaScript objects and their \lambdajs representations are
correctly formed. The invariants are split into two relations, where one
involves the evaluation contexts, and the other the heaps. Both of these involve
the bisimulation relation, but the context invariant uses it only positively. As
the bisimulation relation only grows during the evaluation (as new objects are
created but objects are never collected), this makes it possible to keep the
proofs simple.

@@

We prove many lemmas about the different language constructs
of JavaScript, including the internal ``specification functions''
(e.g., type conversions, operations on objects and environment
records, etc.). Typically, the proof for a lemma consists of
a series of forward reasoning steps and case analyses, and ends with
constructing a JSCert semantics derivation and proving that
the invariants were preserved. The forward reasoning is largely
automated using domain-specific tactics; the JSCert derivation
is constructed using the \texttt{eauto} tactic with a specialized
hint database (\texttt{nocore} is used to avoid using the standard
hints coming from Coq and Chargu\'eraud's TLC
library,\footnote{\url{http://www.chargueraud.org/softs/tlc/}} which is
used both by JSCert and our development).

@@

In the course of our work, we found numerous cases where
\lambdajs did not faithfully follow the ES5 
specification.\footnote{\url{https://github.com/tilk/LambdaCert/wiki/Issues-with-LambdaS5}}
Some of these issues were serious enough that
far-reaching changes in the \lambdajs environment were needed
to solve them. Interestingly, no serious issues in JSCert were
found, which strengthens our confidence that it accurately models
the ES5 specification.

While proving the correctness of while loops, we found an interesting
inconsistency between the ES5 specification and the behavior
of the two most popular JavaScript implementations, Google's V5 and
Mozilla's SpiderMonkey. The discovery of the inconsistency,
which involves exceptions and statement result values,
resulted in a correction being made in the official ES6
specification.\footnote{\url{https://esdiscuss.org/topic/loop-unrolling-and-completion-values-in-es6}}
\asi{We should detail the bug.}

@@

%%% Local Variables:
%%% coding: utf-8
%%% TeX-engine: xetex_sh
%%% End:
